---
title: "Art History - TidyTuesday"
author: "Kristen Howard"
date: "`r Sys.Date()`"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(
  echo = TRUE,
	fig.path = "../Output/",
	message = FALSE,
	warning = FALSE
)
```

# Load Packages
```{r}

library(tidytuesdayR)
library(tidyverse)
library(here)
library(ggplot2)

```


# Load Data
```{r cars}
artists <- readr::read_csv('https://raw.githubusercontent.com/rfordatascience/tidytuesday/master/data/2023/2023-01-17/artists.csv')
# Load in data
```

# Observe Data

```{r pressure, echo=FALSE}
view(artists) # Check data
summary(artists)
```

I am interested in highlighting the lack of diversity in this data set. First, let's get a number of artist race and name them with a corresponding dataframe.

Number of black or African american artists present

```{r}
df2 <- artists %>% # Select data set
         select(artist_name,artist_race, artist_ethnicity) %>% # Select variables of interest
         filter(artist_race == 'Black or African American') %>% # Filter by variable of interest
         unique() %>% # Remove duplicates
         count(artist_race) # total number
                        
view(df2) # There are 18 artists present


```

Number of white artists presents in data set
```{r}
df3 <- artists %>% # Select data set
        select(artist_name,artist_race) %>% # Select variables of interest
        filter(artist_race == 'White') %>% # Filter by variable of interest
        unique() %>% # Remove Duplicates
        count(artist_race) # Total number
view(df3)  # There are 350 white artists
```

Number of Native Hawaiian or Other Pacific Islander
```{r}
df4 <- artists %>% # Select data set
        select(artist_name,artist_race) %>% # Select variables of interest
        filter(artist_race == 'Native Hawaiian or Other Pacific Islander') %>% #Filter by variable of interet
        unique() %>% # Remove duplicates
        count(artist_race)
view(df4) # There are 6 Native Hawaiian or Other Pacific Islander artists
```


# Create a datafrane with the values calculated above

```{r}
data <- data.frame(
  Race=c("Black or African American", "Native Hawaiian or Other Pacific Islander", "White"),
  count=c(18, 6, 350)
)
```


```{r}
data$fraction <- data$count / sum(data$count)# Calculate percentages
data$ymax <- cumsum(data$fraction) # Compute the cumulative percentages (top of each rectangle)
data$ymin <- c(0, head(data$ymax, n=-1))# Compute the bottom of each rectangle
data$labelPosition <- (data$ymax + data$ymin) / 2 # Compute label position
data$label <- paste0(data$Race, "\n value: ", data$count)# Compute a good label

```

### Now create the plot. I tried moving the artist race around on the graph, but it it is not working. I have spent several hours on this so I will be submitting what I have. Additionally, I tried adding a title with the *labs()* function and it did not work.

```{r Graph of Artist Race in Dataset}
ggplot(data, aes(ymax=ymax, ymin=ymin, xmax=2, xmin=3, fill=Race)) + 
  geom_rect() +
  geom_text( x=4.5, aes(y=labelPosition, label=label, color=Race), size=4) + # x here controls label position (inner / outer)
  scale_fill_brewer(palette=13) +
  scale_color_brewer(palette=13) +
  coord_polar(theta="y") +
  xlim(c(-1, 4)) +
  theme_void()

```

